Verifying Spatial Properties of Stencil Computations

### 2016-11-16 paper.tex
Further simplify related work

Various deductive verification tools can express array indexing
in their specifications, \eg{}, ACSL of \citet{baudin2008acsl}
for C (see \eg{}~\citet[Example 3.4.1]{burghardt2010acsl}). Thus, a specification
can be given for a stencil computation, 
however, such a specification would exactly replicate the fine-grained
indexing seen in the code and would be similarly prone to low-level input
errors. Our approach is much more abstract-- it does
not aim to reify indexing in the specification, but is novel
in that it instead
provides abstract spatial descriptions which capture a large number
of common patterns.

>>>>

Various deductive verification tools can express array indexing
in their specifications, \eg{}, ACSL of \citet{baudin2008acsl}
for C (see \eg{}~\citet[Example 3.4.1]{burghardt2010acsl}). A specification
can be given for a stencil computation, 
however, such specification would replicate the fine-grained
indexing seen in the code and would be similarly prone to indexing
errors. Our approach is much more abstract-- it does
not aim to reify indexing in the specification, but
provides simple spatial descriptions which capture a large number
of common patterns.
